---
title: "Cantabria Monuments Shiny App"
author: "Laro Navamuel"
date: "13 de agosto de 2018"
output:
  revealjs::revealjs_presentation:
    theme: sky
    highlight: pygments
    center: false
    self_contained: true
    reveal_options:
      slideNumber: true
      previewLinks: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```
##Project Assignment
This peer assessed assignment has two parts. 

-First, you will create a Shiny application and deploy it on Rstudio's servers. 
-Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

Your Shiny Application

 1.Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using  your application.
 2.Deploy the application on Rstudio's shiny server
 3.Share the application link by pasting it into the provided text box
 4.Share your server.R and ui.R code on github

The application must include the following:

 1.Some form of input (widget: textbox, radio button, checkbox, ...)
 2.Some operation on the ui input in sever.R
 3.Some reactive output displayed as a result of server calculations
 4.You must also include enough documentation so that a novice user could use your application.
 5.The documentation should be at the Shiny website itself. Do not post to an external link.


## Project Presentation

Main subject of this project is create a Shiny App made in R with Shiny.
"Take a fresh, interactive approach to telling your data story with Shiny. Let users interact with your data and your analysis. And do it all with R.
Shiny is an R package that makes it easy to build interactive web apps straight from R. You can host standalone apps on a webpage or embed them in R Markdown documents or build dashboards. You can also extend your Shiny apps with CSS themes, htmlwidgets, and JavaScript actions. 


## The subject


North of Spain, and more specifically Cantabria,has a considerable amount of monuments.
Is more remarkable taking into consideration total surface of this small state, compared to others in Spain.
Vast majority of monuments are religious, but one in special is famous, is Altamira Caves, named Prehistoric Sixtine chapelle for his unique caracteristics and paintings.

This shiny app allows the user have a tool to explore and locate all monuments of all kind in Cantabria.

## The project elements



The project is built based in two elements:
-An interactive app made with Shiny
-This presentation built with R Presenter.

Interactive application is made into a shiny dashboard, on left side panel exist a dropdown list with all regions where Cantabria has monuments.
The output is a map built with Leaflet, showing location and description of monuments located in the user selected regions.
By default all regions are selected and showed on leaflet map.

The application can be found in this address: [Cantabria Monuments App](https://padawone.shinyapps.io/shinyapp/) 

The code is located on GitHub Repository: 


## The Code

```{r reading Data,echo=TRUE}

library(dplyr)
library(tidyr)
library(stringr)

# Read data
Cant_Patrimonio <- read.csv("./ShinyApp/data/Patrimonio.csv", encoding="UTF-8",sep=";",header=TRUE,stringsAsFactors = FALSE)

#Our coordinates are in Grades Minutes and Seconds, is needed to transform into decimal grades, but first
#separate data into latitud and longitude.
Cant_Patrimonio$Grados_Lat <- matrix(unlist(str_sub(Cant_Patrimonio$Coordenadas,start=1,end = 10)), ncol=1, byrow=TRUE)
Cant_Patrimonio$Grados_Long <- matrix(unlist(str_sub(Cant_Patrimonio$Coordenadas,start=-10)), ncol=1, byrow=TRUE)

#(23° 08' 06'' N) = (23 + (08 / 60) + (06 / 3600)) = 23.134999
#If coordinates are South or West values are negative.

if (str_sub(Cant_Patrimonio$Grados_Lat,start=10,end=10) =='N') {
        Cant_Patrimonio$Latitud <- as.numeric(str_sub(Cant_Patrimonio$Grados_Lat,start=1,end=2)) + as.numeric(str_sub(Cant_Patrimonio$Grados_Lat,start=4,end=5))/60 + as.numeric(str_sub(Cant_Patrimonio$Grados_Lat,start=7,end=8))/3600
        
} else {
        Cant_Patrimonio$Latitud <- as.numeric(str_sub(Cant_Patrimonio$Grados_Lat,start=1,end=2)) + as.numeric(str_sub(Cant_Patrimonio$Grados_Lat,start=4,end=5))/60 + as.numeric(str_sub(Cant_Patrimonio$Grados_Lat,start=7,end=8))/3600
        Cant_Patrimonio$Latitud <- Cant_Patrimonio$Latitud *-1
}

if (str_sub(Cant_Patrimonio$Grados_Long,start=10,end=10) =='E') {
        Cant_Patrimonio$Longitud <- as.numeric(str_sub(Cant_Patrimonio$Grados_Long,start=2,end=2)) + as.numeric(str_sub(Cant_Patrimonio$Grados_Long,start=4,end=5))/60 + as.numeric(str_sub(Cant_Patrimonio$Grados_Long,start=7,end=8))/3600
        
} else {
        Cant_Patrimonio$Longitud <- as.numeric(str_sub(Cant_Patrimonio$Grados_Long,start=2,end=2)) + as.numeric(str_sub(Cant_Patrimonio$Grados_Long,start=4,end=5))/60 + as.numeric(str_sub(Cant_Patrimonio$Grados_Long,start=7,end=8))/3600
        Cant_Patrimonio$Longitud <- Cant_Patrimonio$Longitud *-1
}


drops <- c("Coordenadas","X","Licencia_Imagenes","Grados_Lat","Grados_Long")
clean_Cant_Patrimonio <- Cant_Patrimonio[ ,!(names(Cant_Patrimonio) %in% drops)]



# We need to draw a map with the localization of the events, so we remove observations 
# with no latitude or longitude
clean_Cant_Patrimonio <- clean_Cant_Patrimonio %>% subset(!is.na(Latitud) & !is.na(Longitud) & !is.na(Poblacion))

# Then we get the list of regions
Regions <-clean_Cant_Patrimonio$Poblacion %>% unique() %>% sort() 


# At last, we display only the main columns
DisplayedColumns <- c("X.U.FEFF.Nombre","Tipo","Categoria","Municipio","Poblacion")

```

## About the data

There is no prepared data or public REST service where monuments information of Cantabria become available.
Information used in this project is built from information extracted from Wikipedia and other fonts.
Some of the monuments don´t have coordinates assigned this is why not all are showed in map, also are regions with monuments but without city, for
efficiency purposes creating the map on visualization layer, records with missing information on cities and coordinates are removed.

